Heatmaps of pleiotropy test statistics

### 2019-07-22 analysis/paper/figures.Rmd
added figs and renamed Rmd file

@@

@@

@@

@@

@@

@@

>>>>

```{r scatter-2}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.05)
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = file.path("../figures", fnsvg))
ggsave(plot = p, filename = file.path("../figures", fnpdf))
```

@@

## Scatter: index v QTL peak position

```{r index-v-peak-position-2}
tibble(symbol = rownames(pm[indic_nonlocal, indic_nonlocal])[ord_nonlocal], index = 1:length(symbol)) %>%
  left_join(nonlocal_annot, by = "symbol") %>%
  ggplot() + geom_point(aes(y = pos, x = index))
```

@@

```{r scatter-5, ref.label="scatter-2"}
```

@@

## Scatter: index v QTL peak position

```{r ref.label = "index-v-peak-position-2"}
```

@@

```{r scatter-7, ref.label="scatter-2"}
```

@@

```{r scatter-11, ref.label="scatter-2"}
```

@@

```{r scatter-13, ref.label="scatter-2"}
```
